\LARGE \bf Machine Translation for Tibetan Buddhist Texts

### 2021-04-14 paper/main.tex
Update main.tex

(Rahul) "PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER
PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER
PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER
PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER
PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER
PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER PLACEHOLDER

@@

(Rahul)

>>>>

This paper’s presents our attempt at training a model focusing on the translation of religious Tibetan texts to the English language. Tibetan is an extremely low-resource language and presents its own unique challenges in every stage toward the development of a high accuracy model. We look to explore ethical considerations of translating religious texts, provide an in-depth view of our procedure and follow up with discussions, results and conclusions. In support, we utilize various resources including conversations with a native speaker and the exploration of open source parallel Tibetan corpuses.

@@

As mentioned in the beginning, developing a machine learning model for Tibetan Buddhist texts is a challenging case study primarily due to the extremely low resources available. We overcame many obstacles while training our model and even employed the usefulness of native speakers along with publicly available resources, but our 6 layer transformer model with switch out was unsuccessful at translating religious Tibetan to English. The translated output does not match closely enough in either pure accuracy or in the meaning of the passage to be useful in translating religious Tibetan texts to English, as expanded upon in the results section. Additionally, we explored the ethical considerations of translating such texts and deeply reflected on those, amongst our procedure and findings.
